  \item \field{Feasibility for Real-World Use}

    \textbf{Production and deployment.} The device is assembled from commodity,
    off-the-shelf parts --- a two-way mirror, a flat display, a single-board computer,
    a camera, and a microphone/speaker --- which keeps the bill of materials low and
    avoids dependence on any custom hardware. Deployment is a single fixed
    installation in the home (bathroom or hallway), with no wearable to lose and no
    ongoing device management demanded of the user. Prior smart-mirror systems built
    from comparable components demonstrate that the form factor is buildable
    today~[9, 10].

    \textbf{Privacy and trust by design.} Because the device includes a camera and
    microphone in the home of a cognitively vulnerable person, trust is a
    prerequisite for adoption, and privacy concerns are a documented barrier to
    assistive-technology uptake~[16, 19]. Our design commitment is on-device
    processing of video and audio, minimal data retention, no cloud streaming of
    faces, and clear controls for the user and their family. This is a designed-in
    strength, not an afterthought.

    \textbf{Adoption strategy.} Abandonment of assistive technology is driven by
    complexity, poor usability, and lack of support~[17, 18]. We address these
    directly through co-design with users and caregivers, a deliberately simple
    interface that avoids deep menus, and a light training and support pathway ---
    all identified in the literature as the factors that make adoption
    stick~[17, 20].

    \textbf{Cost effectiveness and who pays.} The strongest economic argument is
    avoided or delayed cost of care: every period a person remains safely
    independent, and every hour of caregiver supervision reclaimed, has a real value.
    Likely payers are family caregivers, disability foundations and
    vocational-rehabilitation programmes, and --- through the employment quota and its
    associated funds --- employers and public agencies, rather than the person with a
    disability directly.

    \textbf{Scaling, sustainability, and partnerships.} A commodity-hardware,
    software-defined product scales through manufacturing and software updates rather
    than bespoke engineering. Partnerships give both a distribution route and the pilot
    data needed to validate impact and secure funding --- public: the Department of
    Empowerment of Persons with Disabilities and community health services; private:
    employers under the disability quota and technology suppliers; community: disability
    foundations, vocational-rehabilitation centres, and caregiver networks.
