  \item \field{Impact on People with Disabilities and Society}

    \textbf{Reduced barriers in daily life.} The mirror's core function is to make
    daily routines reliable without a caregiver present. Prompting technology has
    been shown in a randomised controlled trial to reduce the human support people
    with acquired brain injury need to complete activities of daily living~[11], and
    scoping reviews confirm gains in independent completion of multistep tasks~[12].
    We target a measurable reduction in missed medication doses and in the time and
    assistance needed to complete a daily routine.

    \textbf{Increased access to work and income.} The starting point is stark: only
    36.3\% of working-age people with disability in Thailand are employed, and just
    8\% reach the competitive labour market~[3, 4]. Because assistive technology has
    been shown in systematic review to improve employment outcomes for people with
    cognitive disability~[14], and prompting systems improve job task completion and
    accuracy~[14, 15], the mirror's path from daily independence to work-task
    prompting is a credible route to raising participation above that baseline.

    \textbf{Greater participation and dignity.} A non-stigmatising device that looks
    like ordinary furniture --- not a medical monitor --- supports autonomy and social
    participation rather than signalling dependence. And by reducing the need for
    constant supervision, it frees family caregivers' time, supporting their own
    capacity to stay in or return to paid work.

    \textbf{Expected quantitative outcomes (pilot targets).} As a Round-1 concept,
    these are measurable objectives to be validated in prototype testing, not results
    already obtained: a reduction in missed medication doses; a reduction in the time
    and assistance needed to complete a defined daily routine (task-time reduction is
    the clean, precedented metric~[11, 15]); an increase in independent completion of
    trained work-task sequences; caregiver time reclaimed per week; and reach across
    the cognitive-disability segment of Thailand's approximately 855{,}000 working-age
    people with disability~[3].

    \textbf{Honest note on the evidence.} Current smart-mirror and prompting evidence
    is strong for short-term independence but thinner on long-term employment
    retention~[13]. Our pilot is designed specifically to begin closing that gap ---
    which is itself part of the project's contribution.
