  \item \field{Project Objectives}

    \begin{enumerate}
      \item To support independent daily living for adults with cognitive and memory
        disability through ambient, always-on prompting --- medication reminders,
        temporal orientation, and step-by-step task guidance --- with no device to
        carry and no app to remember to open.
      \item To build from daily independence toward employability by extending the
        same prompting to work-related task sequences and routines, so that the
        innovation supports not only living but learning and earning.
      \item To reduce the daily supervision burden on family caregivers, freeing
        their time and supporting their own ability to remain in paid work.
      \item To deliver this through an affordable, non-stigmatising, privacy-by-design
        device suitable for real homes and, in future, supported workplaces in Thailand.
    \end{enumerate}

  \item \field{Target Users}

    \textbf{Primary users.} Working-age adults with cognitive or memory disability
    who live independently or semi-independently and want to build or keep their
    autonomy --- and, where possible, employment.
    \begin{itemize}
      \item \textbf{Disability type / accessibility need:} intellectual disability;
        traumatic brain injury; post-stroke cognitive impairment; early-onset
        dementia. The shared, addressable need is impairment of memory, attention,
        and executive function~[5, 7, 8].
      \item \textbf{Age range:} working-age adults, 15--59.
      \item \textbf{Usage context:} the home, positioned at a fixed point in the
        daily routine (bathroom or hallway); designed to extend into supported
        employment settings in a later phase.
      \item \textbf{Estimated number of target users:} of roughly 855{,}000
        working-age people with disability in Thailand, the cognitive-disability
        segment (intellectual plus mental or behavioural, about 312{,}000
        registered) represents the core addressable group, in the tens of
        thousands even under conservative reach assumptions~[2, 3].
      \item \textbf{Secondary users:} family caregivers (who benefit from reduced
        supervision load) and, prospectively, job coaches and supported-employment
        providers.
      \item \textbf{Related organisations / communities:} the Department of
        Empowerment of Persons with Disabilities, disability-focused foundations
        and vocational-rehabilitation centres, community health services, and
        employers participating in the disability employment quota.
    \end{itemize}
