  \item \field{References}

    {\footnotesize
    \setlength{\columnsep}{1.2em}
    \begin{multicols}{2}
    \begin{enumerate}[label=\arabic*.,leftmargin=1.5em,itemsep=0pt,parsep=0pt,topsep=0pt]
      \item Wattanadumrong B., Chaiboonsri C., Kadthan W. (2026). The Effects of Disability on Household Income and Poverty in Thailand: Evidence from the Socioeconomic Survey. \emph{Economies}, 14(5), 169. doi:10.3390/economies14050169
      \item National Assembly of Disability Thailand (NADT) (2022). \emph{Report on Disability Situation in Thailand 2565}. Department of Empowerment of Persons with Disabilities (DEP). https://nadt.or.th/en/stat65.html
      \item National Statistical Office of Thailand \& UNICEF Thailand (2023). \emph{The 2022 Disability Survey}. Bangkok: NSO/UNICEF.
      \item Cheausuwantavee T., et al. (2021). Employment for Persons with Disabilities in Thailand: Opportunities and Challenges in the Labor Market. \emph{Journal of Population and Social Studies}.
      \item Wolf T.J., Doherty M., Boone A., Rios J., et al. (2019). Cognitive oriented strategy training augmented rehabilitation (COSTAR) for ischemic stroke: a pilot exploratory randomized controlled study. \emph{Disability and Rehabilitation}, 43(2), 201-210. doi:10.1080/09638288.2019.1620877
      \item Government of Thailand (2007). \emph{Persons with Disabilities Empowerment Act B.E. 2550}, Sections 33--35 (employment quota and concessions).
      \item Cunningham L.J., Stapleton T., Walsh K., Horgan F. (2026). Post-stroke cognitive impairment is associated with poorer return-to-work outcomes in working-aged stroke survivors: A systematic review. \emph{Clinical Rehabilitation}. doi:10.1177/02692155261420770
      \item Cuthbert J.P., Harrison-Felix C., Corrigan J.D., Bell J.M., et al. (2015). Unemployment in the United States After Traumatic Brain Injury for Working-Age Individuals. \emph{Journal of Head Trauma Rehabilitation}, 30(3), 160-174. doi:10.1097/HTR.0000000000000090
      \item Kang B.R., Bae Y.H., Park S.H., Kang H.Y. (2025). Feasibility of a developed cognitive training system based on virtual reality with smart mirror for expert in community older cognitive disabled persons setting. \emph{Journal of Alzheimer’s Disease}, 105(2), 598-608. doi:10.1177/13872877251330147
      \item Chaparro J.D., Ruiz J.F.B., Romero M.J.S., Peño C.B., et al. (2021). The SHAPES Smart Mirror Approach for Independent Living, Healthy and Active Ageing. \emph{Sensors}, 21(23), 7938. doi:10.3390/s21237938
      \item O'Neill B., Best C., O'Neill L., Ramos S.D.S., et al. (2018). Efficacy of a Micro-Prompting Technology in Reducing Support Needed by People With Severe Acquired Brain Injury in Activities of Daily Living: A Randomized Control Trial. \emph{Journal of Head Trauma Rehabilitation}, 33(5), E33-E41. doi:10.1097/HTR.0000000000000358
      \item Stierle J., Ryan J.B., Katsiyannis A., Mims P., et al. (2023). Using smart phone technology to improve daily living skills for individuals with intellectual disabilities. \emph{Journal of Applied Research in Intellectual Disabilities}, 36(5), 1169-1178. doi:10.1111/jar.13139
      \item Milhem-Midlej T., Szpiro S.F. (2025). Can video prompting be used to teach employment skills to older adults with moderate to moderate-severe intellectual developmental disabilities?. \emph{Research in Developmental Disabilities}, 166, 105112. doi:10.1016/j.ridd.2025.105112
      \item Sauer A.L., Parks A., Heyn P.C. (2010). Assistive technology effects on the employment outcomes for people with cognitive disabilities: A systematic review. \emph{Disability and Rehabilitation: Assistive Technology}, 5(6), 377-391. doi:10.3109/17483101003746360
      \item Mihailidis A., Melonis M., Keyfitz R., Lanning M., et al. (2015). A nonlinear contextually aware prompting system (N-CAPS) to assist workers with intellectual and developmental disabilities to perform factory assembly tasks: system overview and pilot testing. \emph{Disability and Rehabilitation: Assistive Technology}, 11(7), 604-612. doi:10.3109/17483107.2015.1063713
      \item Yusif S., Soar J., Hafeez-Baig A. (2016). Older people, assistive technologies, and the barriers to adoption: A systematic review. \emph{International Journal of Medical Informatics}, 94, 112-116. doi:10.1016/j.ijmedinf.2016.07.004
      \item Thordardottir B., Malmgren Fänge A., Lethin C., Rodriguez Gatta D., et al. (2019). Acceptance and Use of Innovative Assistive Technologies among People with Cognitive Impairment and Their Caregivers: A Systematic Review. \emph{BioMed Research International}, 2019, 1-18. doi:10.1155/2019/9196729
      \item Randall K.N., Drew H., Gilman E.S., Dixon E. (2024). Assistive Technology Uses and Barriers in the Home and Workplace for Adults With Intellectual and Developmental Disabilities. \emph{Journal of Applied Research in Intellectual Disabilities}, 38(1). doi:10.1111/jar.13306
      \item Pal D., Zhang X., Siyal S. (2021). Prohibitive factors to the acceptance of Internet of Things (IoT) technology in society: A smart-home context using a resistive modelling approach. \emph{Technology in Society}, 66, 101683. doi:10.1016/j.techsoc.2021.101683
      \item Liu L., Stroulia E., Nikolaidis I., Miguel-Cruz A., et al. (2016). Smart homes and home health monitoring technologies for older adults: A systematic review. \emph{International Journal of Medical Informatics}, 91, 44-59. doi:10.1016/j.ijmedinf.2016.04.007
    \end{enumerate}
    \end{multicols}
    }
